Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-18 cvx-flats-neurips21/cvx-flats.tex
Updating figs to be more uniform
And figs are in table format

\section{Illustration: geometric intuition for the four quadrants}
We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants.
This is demonstrated in Figure~\ref{tab:illustrate-quadrant-apps}.

\begin{figure}
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.05,...,1}
{
	\pgfmathsetmacro\aa{\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(\aa,1-\aa,2)$);
	\draw[myblue,thin] (A) -- (B);
}
\draw[orange, very thick,dashed] (0.3,0.7,0) -- (0.3,0.7,2);
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node[inner sep=2pt] (levset1) at (0.3,0.7,-.3) {$\Gamma_{0.4}\!\!$};
%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
\placefiglabel{(Q3)}
\end{tikzpicture}
\hfill
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.1,...,1}
{
	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
	\pgfmathsetmacro\bb{0.5*\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(1-\aa,\aa,0)$);
	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
	\draw[myblue,thin] (C) parabola (A);
	\draw[myblue,thin] (C) parabola (B);
}
\def\c{0.8}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\coordinate (A) at ($(\aa,1-\aa,0)$);
\coordinate (B) at ($(1-\aa,\aa,0)$);
\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
\draw[myorange, very thick] (C) parabola (A);
\draw[myorange, very thick] (C) parabola (B);
\draw[myorange, dashed] (A) -- (0,1/3,2/3);
\end{scope}
\def\c{0.8}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.8}$};
\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
\placefiglabel{(Q4)}
\end{tikzpicture}
\hfill
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
\draw[myorange, dashed] (1/2,0,1/2) -- (0,1,0);
\draw[myorange, dashed] (2/3,1/3,0) -- (0,1/3,2/3);
\node (uniformdot) at (1/3,1/3,1/3) {$\bullet$};
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\Gamma_{1}$};
\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\Gamma_{\bot}$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
\placefiglabel{(Q1)}
\end{tikzpicture}
\hfill
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\draw[myblue,thin] (1/4,0,3/4) -- (0,1/4, 3/4);
\draw[myblue,thin] (1/8,1/8,3/4) -- (1/2, 1/2,0);
\def\e{1/16};
\draw[orange, dashed] (1/8 + \e, 0, 1 - 1/8 - \e) -- (0, 1 - 1/8 - \e, 1/8 + \e);
\draw[orange, dashed] (1/2 + \e, 1/2- \e, 0) -- (\e, 0,1- \e);
\node (point) at (1/8 + \e, 1/8 -\e/2, 3/4 - \e/2) {$\bullet$};
%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node[inner sep=2pt] (levsetmin1) at (1/2, 1/4,1/4) {$\Gamma_{-1}$};
\node[inner sep=2pt] (levset1) at (1/4,1/2,1/4) {$\Gamma_{1}\!\!$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
\placefiglabel{(Q2)}
\end{tikzpicture}
\end{figure}
%\end{tabular}\label{tab:quadrants-simplices}
%\end{figure}

>>>>

\section{Illustration: geometric intuition for the four quadrants}
We can apply Lemma~\ref{lem:convex-flats-inf-dim} to construct lower bounds on convex consistency dimension for targets across all four quadrants by Corollaries~\ref{cor:Pcodim-flat-elic-relint-prop} (for discrete prediction problems; Q1, Q2) and~\ref{cor:Pcodim-flat-single-val-prop} (for continuous estimation problems; Q3, Q4).
This is demonstrated in Table~\ref{tab:illustrate-quadrant-apps}.

\begin{table}
\begin{tabular}{|c|c|}
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
	\draw[myorange, dashed] (1/2,0,1/2) -- (0,1,0);
	\draw[myorange, dashed] (2/3,1/3,0) -- (0,1/3,2/3);
	\node (uniformdot) at (1/3,1/3,1/3) {$\bullet$};
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\Gamma_{1}$};
	\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\Gamma_{\bot}$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q1)}
	\end{tikzpicture}
	&
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue,thin] (2/3,0,1/3) -- (0,2/3, 1/3);
	\def\e{1/16};
	\draw[myblue,thin] (\e + 1/3, 1/3- \e,1/3) -- (1/2 + \e, 1/2 - \e,0);
	\coordinate (point) at (1/3 - \e/2, 1/3 + \e, 1/3 - \e/2);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[orange, dashed] (2/3 + \e/2,0,1/3 - \e/2) -- (0,2/3 + \e/2, 1/3 - \e/2);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\Gamma_{-1}\!\!$};
	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\Gamma_{1}\!\!$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
	\end{tikzpicture}
	\\
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.05,...,1}
{
	\pgfmathsetmacro\aa{\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(\aa,1-\aa,2)$);
	\draw[myblue,thin] (A) -- (B);
}
\draw[orange, very thick,dashed] (0.5,0.5,0) -- (0,0.,2);
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node (centerdot) at (1/3,1/3,1/3) {$\bullet$};
\node[inner sep=2pt] (levset1) at (0.5,0.5, -0.3) {$\Gamma_{0}\!$};
%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.5,0.5,0);
\placefiglabel{(Q3)}
\end{tikzpicture}
&
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.1,...,1}
{
	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
	\pgfmathsetmacro\bb{0.5*\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(1-\aa,\aa,0)$);
	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
	\draw[myblue,thin] (C) parabola (A);
	\draw[myblue,thin] (C) parabola (B);
}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\coordinate (A) at ($(\aa,1-\aa,0)$);
\coordinate (B) at ($(1-\aa,\aa,0)$);
\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
\coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
\coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
\coordinate (centerdot) at (0.3,0.3, 0.4);
\draw[myorange, very thick] (C) parabola (A);
\draw[myorange, very thick] (C) parabola (B);
\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (3/4,0,1/4) -- (centerdot);
\node at (centerdot) {$\bullet$};
\end{scope}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.6}$};
\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
\placefiglabel{(Q4)}
\end{tikzpicture}
\end{tabular}\label{tab:quadrants-simplices}
\caption{Example properties for each of the 4 quadrants and how we can or cannot fit $1$-flats through the level sets containing $p = \bullet$. \jessie{TODO: ADD MORE}}
\end{table}
